A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Wrote a bit more about our heuristics

Small scale experiments (not presented here) were performed to identify
suitable heuristics for selecting a label class and a vertex within a label
class. Our heuristic of choice selects the label class with the
smallest $\max(|\setG|,|\setH|)$. From this class, a vertex with maximum degree
is selected from $\setG$. We discuss this further in \cref{sec:comparison}.

>>>>

Small scale experiments (not presented here) were performed to identify
suitable heuristics for the $\FuncSty{SelectLabelClass}$ and
$\FuncSty{SelectVertex}$ functions.  Our $\FuncSty{SelectLabelClass}$
function chooses a label class with the smallest $\max(|\setG|,|\setH|)$,
breaking ties by selecting a class containing a vertex in $G$ with the largest degree. From
the selected class, $\FuncSty{SelectVertex}$ chooses a vertex in $\setG$ with
maximum degree. We further discuss the effectiveness of our
$\FuncSty{SelectLabelClass}$ function in \cref{sec:comparison}.
